### 2019-09-06 README.Rmd
Remove binder

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/nfrerebeau/archeosciences2019/master?urlpath=rstudio)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2613512.svg)](https://doi.org/10.5281/zenodo.2613512)
[![GitHub Release](https://img.shields.io/github/release/nfrerebeau/archeosciences2019.svg)](https://github.com/nfrerebeau/archeosciences2019/releases)
[![Travis-CI Build Status](https://travis-ci.org/nfrerebeau/archeosciences2019.svg?branch=master)](https://travis-ci.org/nfrerebeau/archeosciences2019)

@@

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("nfrerebeau/archeosciences2019")
```

>>>>

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2613512.svg)](https://doi.org/10.5281/zenodo.2613512)
[![GitHub Release](https://img.shields.io/github/release/nfrerebeau/archeosciences2019.svg)](https://github.com/nfrerebeau/archeosciences2019/releases)
[![Travis-CI Build Status](https://travis-ci.org/nfrerebeau/archeosciences2019.svg?branch=master)](https://travis-ci.org/nfrerebeau/archeosciences2019)

@@

```{r gh-installation, eval=FALSE}
# install.packages("devtools")
remotes::install_github("nfrerebeau/archeosciences2019")
```
